Carbonate chemistry at Ny-Ålesund

### 2023-03-03 awipev-CO2.Rmd
minor fig change

```{r, echo=FALSE, message= FALSE, warning=FALSE}
g <- (at_s | pco2_calc_meas) / (offset_ph | pHspec_pHseafet)
g <- g + patchwork::plot_annotation(tag_levels = 'A') & 
  theme(plot.tag = element_text(face = "bold"))
ggsave(filename = "figures/pco2_ph_etc.png", plot = g)
ggsave(filename = "figures/essd/fig04.pdf", plot = g)
```

>>>>

```{r, echo=FALSE, message= FALSE, warning=FALSE}
g <- (at_s | pco2_calc_meas) / (offset_ph | pHspec_pHseafet)
g <- g + patchwork::plot_annotation(tag_levels = 'A') & 
  theme(plot.tag = element_text(face = "bold"))
ggsave(filename = "figures/pco2_ph_etc.png", plot = g)
ggsave(filename = "figures/essd/pco2_ph_etc.pdf", plot = g)
```
